---
title: "Exploring AIChE 2020 PD2M Sessions"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

I wanted to explore AIChE 2020 [PD2M](https://plan.core-apps.com/aiche2020/events?trackIds=94693210d53140b389648b84df76b433) sessions to understand the following:

* People with high number of talks
* Companies/University with high number of talks
* Mix of industry vs university talks

```{r}
library(gt)
library(dplyr)
library(ggplot2)
```

## Authors with high number of talks

```{r}
top_auth = read.csv("tables/top_auth.csv", stringsAsFactors = FALSE)
top_auth %>% rename(talks = n, affiliation = affil_clean) %>% 
  head(15) %>% gt() %>% opt_row_striping() %>% 
    cols_label(author = md("**author**"),
              talks = md("**talks**"),
              affiliation = md("**affiliation**"))
```

## Companies/Universities with high number of talks

```{r}
top_affil = read.csv("tables/top_affil.csv", stringsAsFactors = FALSE)
top_affil %>% rename(affiliation = affil_clean, talks = n) %>% 
     head(15) %>% gt() %>%
       cols_label(affiliation = md("**Company/University**"),
                  talks = md("**talks**")) %>% opt_row_striping()
```

## Mix of Industry/University Talks

This year the mix of university/industry talks is about 50/50 split between university only talks and industry or industry/university talks. Industry/University talks make up ~20% of the talks.

```{r}
induniv_summary = read.csv("tables/induniv_summ.csv", stringsAsFactors = FALSE)
lbl_map = c("ind only" = "industry", "univ only" = "university", "ind_univ" = "industry/university")
induniv_summary = induniv_summary %>% mutate(type_lbl = lbl_map[type],
                                             pct_talks = paste0(round(n_pct * 100),"%"))
induniv_summary %>% select(type_lbl, pct_talks) %>% gt() %>%
       cols_label(type_lbl = md("**Type**"), pct_talks = md("**% talks**"))
```

## Industry Collaboration Network

Different companies have different academic collaborations. The table below shows the university collaborations for select companies.

```{r}

induniv_collab = read.csv("tables/induniv_collab.csv", stringsAsFactors = FALSE)
induniv_collab = induniv_collab %>% filter(affil_clean %in% c("eli lilly", "abbvie", "pfizer", "astrazeneca", "wuxi"))
induniv_collab %>% select(-cnt) %>% group_by(affil_clean) %>% gt() %>%
       cols_label(affil_clean_univ = md("**University**")) %>%
       tab_style(
         style = list(
             cell_fill(color = "lightblue")
         ),
         locations = cells_row_groups()
       )
```

## Session Mix (Industry vs University Talks)

The table below is sorted in order of % of university only talks: 0% indicating all talks in the session are by industry, 100% indicating all talks in the session are by universities.

```{r}
sort_ind = read.csv("tables/sort_ind.csv", stringsAsFactors = FALSE)
sort_ind = sort_ind %>% mutate(pct_univ = paste0(round(univ.only * 100),"%"),
                               url = paste0("https://plan.core-apps.com", session_url))

# https://community.rstudio.com/t/create-interactive-links-in-gt-table-in-rmarkdown/70266/2
make_hyperlink = function(myurl,mytext="link") {
  paste('<a href="',myurl,'">',mytext,'</a>')
}


sort_ind %>% select(pct_univ, session, url) %>% gt() %>%
  fmt (
    columns = 'url',
    fns = make_hyperlink
  ) %>% cols_label(pct_univ = md("**% University Talks**"),
                   session = md("**session**"),
                   url = md("**url**")) %>% opt_row_striping()
```

## References

* [python code](https://github.com/notesofdabbler/explore_AIChE2020/blob/main/scrape_AIChE2020_PD2M.py) for scraping the PD2M sessions
* [R code](https://github.com/notesofdabbler/explore_AIChE2020/blob/main/explore_AIChE2020_PD2M.R) for exploring the PD2M sessions.